---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bevstat

<!-- badges: start -->
<!-- badges: end -->

The goal of bevstat is to visualize some population data from Statistik Austria.
Especially the population data of Austria from the year 2020,
which can be found [here](https://data.statistik.gv.at/web/meta.jsp?dataset=OGD_bevstandjbab2002_BevStand_2020).

## Installation

You can install the development version from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("MaximilianBernkopf/bevstat")
```

## Example

Via `get_population_data` you can download the relevant data
and have certain internal codes replaced by more useful names.
Alternatively you can also just use the data already available 
in the package:

```{r data example}
library(bevstat)
#population_df <- get_population_data()
population_df
```

Next the function `summarise_population_df` performs some summary statistics.
In particular it takes the data frame returned by `get_population_data` or `population_df` directly 
and calculates the relative size of each age group per commune 
as well as the average age in each commune. 
Note that the information regarding gender is first summarized. 
Furthermore, the state name is added, e.g., "Wien", "Burgenland" etc.

```{r summary data example, message=FALSE}
population_summary_df <- summarise_population_df(population_df)
population_summary_df
```

Finally you may plot the average age per commune vs the proportion of preschool kids as follows

```{r pressure, message=FALSE}
plot_preschool_vs_average_age(population_summary_df)
```

Have fun. 
